Modeling Human Interactions in Collaborative Interactive Evolutionary Computation

### 2017-04-06 2017-GECCO-Modeling-User-Interactions-in-IEC/paper-front.tex
First draft

\author{Mario Garc\'ia-Valdez,\\ Jos\'e-C  Romero}
\affiliation{%
  \institution{Dept. of Graduate Studies,\\ Instituto
Tecnol\'ogico de Tijuana, Tijuana, M\'exico}
  }
\email{(mario|jcromero)tectijuana.edu.mx}

@@

\begin{abstract}
The necessary intervention of humans in interactive evolutionary
computational systems has inherent drawbacks arising from the very nature of 
the algorithms, namely, the human fatigue caused by the interaction, and
the boredom arising when users evaluate a large number of artifacts.
To tackle these issues, in this paper we
propose a human-centered framework to model complex interactions on these systems.
A case study is presented where the model is applied in the 
development of a collaborative evolutionary interactive system. 
% Both conceptual and implementation details are provided where the   
% technique is used to measure and increase user engagement and participation.
% Our experiments show that the model can be successfully applied in a
% gamification technique developed to increase user engagement, which
% implies that this technique can successfully be used to 
% decrease user fatigue and boredom, and thus increase the {\em performance} of the
% interactive system.
\end{abstract}

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below. 
%
\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10003120.10003130.10003233</concept_id>
<concept_desc>Human-centered computing~Collaborative and social computing systems and tools</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10010147.10010178.10010205.10010206</concept_id>
<concept_desc>Computing methodologies~Heuristic function construction</concept_desc>
<concept_significance>300</concept_significance>
</concept>
<concept>
<concept_id>10010147.10010178.10010205.10010207</concept_id>
<concept_desc>Computing methodologies~Bio Inspired Algorithms</concept_desc>
<concept_significance>300</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Human-centered computing~Collaborative and social computing systems and tools}
\ccsdesc[300]{Computing methodologies~Heuristic function construction}
% We no longer use \terms command
%\terms{Theory}

\keywords{Interactive evolutionary computation, Human Centered Computing}

>>>>

\author{Mario Garc\'ia-Valdez, Jos\'e-C Romero}
\affiliation{%
  \institution{Dept. of Graduate Studies,\\ Instituto
Tecnol\'ogico de Tijuana, Tijuana, M\'exico}
  }
\email{mariosky@gmail.com}
\email{josec.romero@tectijuana.edu.mx}

@@

\begin{abstract} The necessary intervention of humans in interactive
evolutionary computational systems has inherent drawbacks arising from the
very nature of the algorithms, namely, the human fatigue caused by the
interaction, and the boredom arising when users evaluate a large number of
artifacts. To tackle these issues, in this paper we propose a human-centered
framework that can be used to  increase volunteer participation in C-IEC 
systems by using gamification techniques. A case study is
presented where the model is applied in the development of a collaborative
evolutionary interactive system.
\end{abstract}

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below. 
%
\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10003120.10003130.10003233</concept_id>
<concept_desc>Human-centered computing~Collaborative and social computing systems and tools</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Human-centered computing~Collaborative and social computing systems and tools}
\keywords{Interactive evolutionary computation, Human Centered Computing}
